Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-28 cav2017/cav2017.tex
wording

\begin{enumerate}
%
\item  We give a novel synthesis algorithm for generating
  state-feedback controllers that are provably stable and in addition
  guaranteee a given safety property. Existing methods for controller
  synthesis rely on transfer function representations, which are
  insufficient to prove safety requirements.
%
\item We give two algorithms: the first, naive one, relies on
  an unfolding of the system's dynamics up to a completeness threshold,
  while the second one is abstraction-based and leverages abstraction
  refinement and acceleration to improve the scalability of the analysis
  while retaining soundness.  Both approaches provide sound synthesis of
  state-feedback systems and consider the various sources of imprecision in
  the implementation of the control algorithm and in the computational
  modeling of plant dynamics.
%
\item We develop a model for different sources of quantization errors and
  their effect on reachability properties.  We give bounds that ensure the
  safety of our controllers in a hybrid continuous-digital domain.
%
\end{enumerate}

>>>>

\begin{enumerate}
%
\item  We compute state-feedback controllers that are provably stable and in
  addition guaranteee a given safety property.  Existing methods for
  controller synthesis rely on transfer function representations, which are
  insufficient to prove safety requirements.
%
\item We give two novel algorithms: the first, naive one, relies on
  an unfolding of the dynamics up to a completeness threshold, while the
  second one is abstraction-based and leverages abstraction refinement and
  acceleration to improve scalability while retaining soundness.  Both
  approaches provide sound synthesis of state-feedback systems and consider
  the various sources of imprecision in the implementation of the control
  algorithm and in the modeling of plant.
%
\item We develop a model for different sources of quantization errors and
  their effect on reachability properties.  We give bounds that ensure the
  safety of our controllers in a hybrid continuous-digital domain.
%
\end{enumerate}
